---
title: "HW3 Solutions"
author: "Rushal Sohal; github: rsohal"
date: "2/18/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
data(tips, package = "reshape2")
```

Q1.
```{r}
numParty <- nrow(tips)
numParty
```
The waiter served 244 parties.

Q2.
```{r}
str(tips)
```

total_bill and tip are Numeric (double here), size is an Integer, and everything else is of type Factor.

Q3.
```{r}
day <- tips$day
day <- day[order(match(day,  c("Thur","Fri","Sat","Sun")))]
day
```

Q4.
```{r}
female5 <- tips[(tips[,7] >= 5) & (tips[,3] == "Female"), ]
female5
```

Q5.
```{r}
library(ggplot2)
ggplot(tips, aes(x=total_bill, y=tip)) + geom_point() + xlab("Total Bill Amount") + ylab("Tip ammount")
```

total_bill and tip have a strong positive correlation. As total_bill increases the tip amount increases and vice-versa.

Q6.

a. There were outliers for some lower amounts of total_bill. For instance, there's a tip of $5+ for a bill of 7-8 USD.

b. As total_bill increases the relationship is less linear and results in a weak correlation (mostly after $20-25 bill amount).

Q7.
```{r}
tips$tiprate <-  tips$tip/tips$total_bill
mean (tips$tiprate)
```
On average, a waiter is tipped 16% of the total bill.

Q8.
```{r}
ggplot(tips,aes(x= factor(tips$time,levels =c("Lunch","Dinner")), y =tiprate))+geom_boxplot()+
xlab("Time")+
ylab("Tip Rate")
```

The average tiprate is about the same, however, Lunch has a larger/wider upper quartile range. Besides, there are some outliers in Dinner.

Q9.
```{r}
tmp <-tips
tmp$new <- paste(tips$sex,tips$smoker)
#made a new column by making a temporary dataset
ggplot(tmp,aes(x =total_bill,y=tip,color = new)) +geom_point()+
xlab("Total Bill Amount")+
ylab("Tip Amount")
```

Non-smokers tend to tip higher for both genders. Males usually have a higher total bill amount.

Q10.
```{r}
ggplot(tips,aes(x=factor(day,levels = c("Thur","Fri","Sat","Sun")),fill=sex))+geom_bar()+
xlab("Day")+
ylab("Number of customers")
```

For weekdays, it's about equal, however, for weekends, more men tend to go to the restaurant.




